\renewcommand{\chaptertitle}{Neuro Psychology}
\setdate{November 6, 2025}
\section{\chaptertitle}

I wasn't taking notes during our meeting today because Oleg
was doing it automatically using an AI tool. After it I went
to KSE to attend Kate's neuro psychology class.

\subsection{Intro}

Kate shortly introduced me to the class. She told me that 
they had psycho-diagnosis course before. Everyone in the 
class is a junior.

Chemical control of brain and behaviour.
Neuremediators, hormons, drugs.

\begin{definition}{Hypothalamus}{}
    It's a part of the brain that lies inside. It produces hormones. 
    It's close to the pituitary. It's close to the intersection
    of nerves from the body.
\end{definition}

periventricular zone?

chiasm -- where eyes' nerves cross.
\begin{enumerate}
    \item suprachiasmatic nucleus (SCN) - circadian rythms
    \item control ANS (autonomous nervous system), regulates outflow of the sympathetic and parasymphathetic innervation of the visceral organs
    \item neurosecretory neurons - to the pituitary gland
\end{enumerate}

pituitary is a gland. it secretes hormons that control all 
the other glands in our body. and hypothalamus is controlling it.

\begin{definition}{Neurohormones}{}
    Hormones that are both hormons and neurotransmitters.
\end{definition}

\textbf{Groups of Hormones}
\begin{enumerate}
    \item Homeostatic
    \item Gonadal
    \item Glucocorticoids
\end{enumerate}

\redtick Insulin is homeostatic one.

corpus callosum regions?

anabolic-androgenic steroids -- the full name of what's widely
known as "steroids".

\textbf{Cortisol \& Stress}

there's a funny guy sitting on the first row in front of me (I'm
sitting in the third row btw) with a strong accent who constantly 
makes comments that make everyone laugh and Kate softly put 
him into quiet.

Neuron is a protein factory, it makes neurotransmitors.

\begin{notebox}
    Synaptic cleft
\end{notebox}

ventral tegmentum?

sympathetic -- stress, parasympathetic -- stress and digest.

the fastest way to get a drug into the brain is to inject is
into the brain itself.

acetylcholine -- is the most widespread neuromediator in the
body.

\redtick tolerance and sensitization. 
so repeated use can make you more reactive to something.
