\startchapter{Monday opener}{Nov 17, 2025}

Not everyone showed up and Rebbecca asked what can do to
fix this issue. Mariia offered to have an agenda for every
meeting and start at the set time not waiting for everyone.

Everyone was low energy. We tried jumping (push-ups were 
offered by Rebbecca initially) but not everyone joined so 
it worked suboptimally. 

\begin{notebox} 
    Every stream must come up with a curriculum chunk(s) 
    from core courses and a way to test them.
\end{notebox}

Mila brought up that since we decided that we will work widthtrimesters in lieu of
semesters we will have to redo our work we did during last two
weeks (almost) from scratch and that will require at least two
more weeks.

Dasha doesn't think that this (semesters changed to 
trimesters) is a big problem.

Masha is afraid that KSE administration may put their foot down
on what we are doing and whether we should run our thing by them
but Rebbecca said that we are not at that stage yet. What we do
now is just the first iteration (out of many). And we can't 
build something novel if we do what we are told to do. This 
means that at some point what we do might be tailored down
and part of our job won't be included in the final result but
it is what it is.

Mariia explained that the problem Mila is talking about is
that engineering team already put timelines (Dasha said "did we
need to do it?" but no-one seemed to hear her) in the curriculum
they developed. And this change (trimesters) spoils it. And 
also that all engineering programs use semesters not trimesters 
and for a reason: to bring about a physical project you need time.

Rebbecca again emphasised that we don't have to create a 
chef d'œvre right now but just the first iteration. Dasha brought
up again that building timetables wasn't a part of the task.

Another problem is that there's no partner student in the
engineering stream. And that causes misalignment and problems.
It was agreed that Ihor and Nadiia will join. Masha stressed 
that people who join should be commited not be like "I'll try
to join\dots will see\dots etc.".

Olexandr said that without majors we can only plan the program 
for two years.

We need to move to testing our own courses.

Side note: I just noticed that "maths and science" has the same
number (34) of credidts allocated as "humanities and arts". 
Scintillating.


