\startchapter{The sync week}{Nov 24, 2025}

Olga will spend more time with our group from now on.
On Friday we will have planning where we will decide what we'll
do in the next sprint (and the rest of this one). And between
today and Friday we have time to finish what we are currently
doing. Olga invited us to a townhall at KSE campus sometime 
this week. And on Thursday we have a workshop with Dmytro
and Nastasia asked us to come to a focus group the same day.

Miro usage propriety was questioned (some people hate it).
The request is: when someone asks to uses some tool, they 
must explain why is it \textit{germane} to the task at hand and a 
short manual explaining how to use it. 
Olga noted that sign Miro is important because she can see 
the way we are thinking and also our Olin counterparts are 
checking on it as a part of our collaboration.
Dasha mantioned that we persnickety about the bigger picture 
when we ought to work on "the meat". The essence is more 
important than the shape.
Dmytro suggested we use less stickers because it becomes
counterproductive. One of the most pressing point is 
miscommunication. Mila brought up the incident when no-one
responded to her request for feedback about the engineering
group's output. Also it was stressed once again that we should
be more responsible, check slack notifications, respond to 
email invitations, react to messages, etc. 

After lunch we gathered to turn our deltas into action points.
I went to a meeting with HR so missed about half an hour of 
their talk.


