\renewcommand{\chaptertitle}{Wednesday}
\setdate{October 1, 2025}
\section{\chaptertitle}

\subsection{Morning debrief at 428}


I was a volunteer to answer questions from Lynn and Zhenya and they were taking post-it notes of what I said.
And then they sticked them to a big piece of paper.

While you are lerning: Look, Ask, Try, Why (soaking) -- this is a framework from Lynn and Zhenya.
You are like a sponge. Fisrst you soak info and experience during day, and then you are squeeed (with these questions as well) so as not to loose anything.

Courage to Teach by Parker Palmer -- a book recommended by Zhenya.
"We teach who we are" -- a quote from it.

Then we discussed what we should do \dots


Around 11:30 to 11:50 I tlked to Dasha about astronomy.
She showed me her thesis and told me in details about it.


\subsection{Think like a biologist}

At the class I met the teacher Jean 
(Rebecca told me about her at lunch).

As a part of a project they are collaborating with a local company that turns 
food waste into compost. they want to see what happens to plastic.
And they need to come up with a method to measure plastic degradation.

\textbf{Principles of Biology}
\begin{enumerate}
    \item Evolution
    \item Structure and function
    \item Info flow, exchange, and storage
    \item Pathways and transformation of energy and matter
    \item Systems
    \item Societal and ethical considerations
\end{enumerate}


3: DNA journey

Jene thinks that we should slow down with CRISPR.

restriction enzymes are used to cut DNA. they are thought to be bacterial immune system.

Explore restriction enzymes: https://nc3.neb.com/NEBcutter/


GFP-producing Plasmid ???

How is the plasmid with the recombinant gene generated?

What are the methods we need to do to put GFP gene into plasmid?


we can order primers for PCR from specialized companies. 
we also might want to add additional restriction sites that are compatible
with restriction enzymes (that don't cut through our gene).

what is electroporation?

primer design is grad level job. 
the cost of synthesis is getting much cheaper.
it might be even cheaper to generate entire plasmid.

to check use PCR again to look for the presence of the gene.

colony PCR?? (might save a lot of times).

Post Lab 1 -- Upcoming (Oct 15)


If I understood correctly we can edit all the genes in our body.

germline and somatic edits.

The Odin company sells DIY CRISPR genome editing kits.

TU 2 (??)

Koeth et al. reading -- adopt a figure sign up

cargo gene, gene drive. can be a lethal gene.

we can make a gene that makes females sterile but can be passed through males.

at 15:00 we split into two groups to discuss whether we should use 
crispr engineered moscitoes. I chose to be in a team that opposes this idea.
in my team there's a girl with curly white hair and blue eyes (don't know her name)
and she debates fiercely. the book "silent spring" was mentioned quite some time.
I think I should read it, it also was in "6 books that changes the world".

\redtick what is MIT extinction invention?

the main arguments were:

- we should use the power we have to help people

and 

- we don't know all the implications

