\renewcommand{\chaptertitle}{Thursday}
\setdate{October 2, 2025}
\section{\chaptertitle}


\subsection{Design Nature}

At 9:30 in the morning we went to the design nature class.
all the time we were doing the prototyping. 
Dasha was checking on us occassionally.

\subsection{Material science}

At 10:55 I with Taya joined the Material Science class.
We were watching a short movie in Chinese with English subtitles.
Then they were discussing it, I didn't get what it was about
because we came about the end of the movie.
After this the teacher said that we have a lab work to do today.
And we went to the lab.

\subsection{Design Better Drugs}

The class started with a strange youtube video with a song about lab sagety rules.

Lab: acid phosphatase assay ??

Cells need energy to drive changes:
\begin{enumerate}
    \item synthetic-biosynthesis-chemical
    \item mechanical work
    \item concentration work
    \item electrical work
    \item heat
    \item bioluminescence
\end{enumerate}

Sometimes RNAs can serve as enzymes too.

Enzymes are catalysts of reactions in cells.

Sometimes there's a series of chem reactions.
So several enzymes are in action.

What is a spontaneous reaction?

What are exorgonic and endorgonic reactions?

What is (non-)competitive inhibitor?


Michaelis-Menten equation: 
$$v=\frac{d[P]}{dt}=\frac{V_{max}[S]}{K_M+[S]}$$

\textbf{What is cancer?}

- cells\\
- cell signaling\\
- cell cycle

In 2011 we went from 6 to 10 hallmarks of cancer and in 2022 we added 4 more (so 14 in total).

Typically, we talk about 5-year survival of cancer as an endpoint.
But doesn't mean the patient is in remission or is cured.

What is uterine corpus?


\subsection{Meeting with Daniel}

At 15:15 I came to a meeting with Daniel and Dasha to discuss Design Nature
class and how we want to split into two groups of four.
