\renewcommand{\chaptertitle}{Thursday}
\setdate{October 9, 2025}
\section{\chaptertitle}


\subsection{Ddesign Nature}

A lecture in the big hall.

Why capture redesign rationale?

- ensure informed decisions

- basis for future decisions within the proj

- basis for future decisions other projects

\subsection{Design Better Drugs}

Another video (we've been up all night to get data -- a get lucky science parody)

\textbf{Today}:
\begin{enumerate}
    \item Wrap up mitosis/meiosis
    \item Cancer treatment
    \item Lab-Stain and view Huvec cells
\end{enumerate}

\textbf{Next week}:
\begin{enumerate}
    \item Genetics
    \item Plate and grow Huvec cells
\end{enumerate}


Hodgkins vs non-Hodgkins lymphoma

- Reed-Sternberg cells

- often begins in neck and then orderly spreads

- typically $15-35$ or $>55$


We have two female visitors (both phd) from Brazil, they are fullbright students

\begin{notebox}
    what is a "G rated show"?
\end{notebox}

\textbf{traditional cancer treatments}:
\begin{enumerate}
    \item surgery
    \item radiation
    \item chemo
\end{enumerate}


Angelina Jolie -- had(has) a predisposition to some specific cancer type that is inherited so she went through a surgery.

adjuvant/neoadjuvant -- after main treatment/before main treatment

Radiation -- focused x-ray beams damage tumor DNA.
Radiation damages cancer cells so badly that the mutation is not advantageous anymore for the cell.

Chemo targets cells that divide fast (and that's why people lose hair -- those are fast-dividing too).

What are microtubules?

There are vaccines. 

Preventative: HPV for genital area, hepatitis to decrease liver cancers, EBV for lymphoma -- in clinical trials.

Treatment$:$ % for some reason it gives a blue wavy underlining if i simply put a colon
provenage for prostate cancer -- approved, 
dendritic cell vaccines for melanoma and othe solid tumors -- in trials.

ELISA -- research tool?

\textbf{Immune Checkpoint Inhibitors}

Cancer puts a protein out that deactivates the immune cell.

PD-L1 -- tells T-cells not to react.

\textbf{Chimeric Antigen Receptor (CAT) T-Cells}

google later what is it because there's little time to note now due to the info load and the upcoming 2 to 1 meeting with Rebecca and Olga.

siRNA in nanoparticles

what is Histotripsy?

The lecture ended here but I didn't make it to the lab because I had a 2 to 1 with Rebecca and Olya at 14:15.
