\renewcommand{\chaptertitle}{Wednesday}
\setdate{October 15, 2025}
\section{\chaptertitle}


\subsection{Human Centered Design}

We had a session about HCD with two invited workshops leaders (Ela and Dan).
At the beginning it wasn't smooth because most people
were (my perception) internally opposed to it but after 
half an hour (and a handful of people have left during that time) it went ok.

\subsection{Think Like a Biologist}

After lunch I joined the Bio class. This is going to be my last offline Bio class here.

\redtick Cellular respiration?

\begin{tipbox}
    use biotech to engineer your microbiome
\end{tipbox}

Metabolism

$$C_6H_{12}O_6 + 6O_2 \rightleftharpoons 6CO_2+6H_2O$$

Algae can photosynthesise.

Salamanders have a synmbiosis with algae (who bring them oxygen).

Joseph Presley put a mouse in a jar.

$$6CO_2+12H_2O \to C_6H_{12}O_6 + 6O_2 +6H_2O$$

oxygen comes from the water (learned from radio lable).

Light RXN: ATP, NADPH (?) (this means to be photosynthetic)

Dark: ATP, NADPH $\to$ Sugars

Clorophile A is green.

\redtick Accessory pigments?

PSII -- photo system 2 (unique bc it is the only thing able to split water into $O_2+2e^{-}+2H^{+}$)

Ferodoxin?

Proton gradient? Potential energy gradient in cells?

People tried to copy PSII and did but not very well. \redtick It would solve all our energy problems.

Rubisco? You can get it from spinach.

\begin{tipbox}
    engineer Rubisco to be more effective to fix carbon better which is important because we have a lot of $CO_2$ in the atmosphere
\end{tipbox}

Calvin Cycle-Benson

$$6CO_2+6RuBP \to (Rubisco +) 12(3PG) \to$$
$$\to (12NADPH + 18ATP +) 10G3P \to Glucose + RuBP$$


$H_2S$ -- hidrogen sulphite, very toxic to us

those who photosynthesise from infrared use this indtead of water

photosynthesis: turn light energy into chemical energy. even if it doesn't produce oxygen

dark reaction: fix carbon

\textbf{photosynthetic sea slug}

it can separate chloroplasts from its food and store them in a special organ in its body. it's hypothesised that it can be photosynthetic.

\redtick kleptoplasty sea slugs



% girls from think like a biologist class
% Adiella Chapa and Arianne Fong -- canadians the second one looks more asian, the first one has something asian too but not so much
% they presented:
\textbf{Improving photosynthesis}


RuBisCO makes a mistake during photorespiration (mistakes oxygen for carbon dioxyde).

photosynthesis evolved when atmosphere was different, less than 5\% efficiency rate

stomata -- "pores" on leaves, currently they are too slow

to be certified as organic you need to certify the soil as organic and if you just use "organic" seeds but grow them purely in water -- not in soil you are not considered organic.


\subsection{MIT}

To access MIT guest WiFi you need to have access to your email to receive the access code. 
Someone has never read Catch-22.

The purpose is to bring together people who are involced\dots

We want to do something about horrible things.

Dmytro Martynovich is the first speaker, CTO at Minesights.

What was the conflict in Sri Lanka??

Second -- UXO Wizard guys who worked during summer in Norway.

And the third one is a demining (military?) professional with 13 (?) years of experience.






