\renewcommand{\chaptertitle}{Research 2}
\setdate{Sepember 8, 2025}

\section{\chaptertitle}

\subsection{Agenda}

9:30-10:00 - Coffee Tea Talk (ask the key at security, room 16)

10:00-11:00 - Intro, updates, delta review

11:00-11:30 - Sync on future research results and intro to HCD tools 

11:30 - 13:00 - Part 1. Teams work on planning research

13:00-14:00 - Lunch

14:00-16:00 - Part 2. Teams work on planning research

16:00- 17:00 - tentative visit by KSE colleagues

\subsection{Goals}

Before we go to Olin we must have the final portrait of the modern engineer and team presentation of our research.

Also manifesto, program descriprion, learning outcomes, culture\dots

For this week:

- have a separate day (Fri) for the culture manifesto 

- the research 

We have to share a few things. Get integrated into Design Nature.

MIT create challenge. Rebecca can do an intro. The plan is to go to MIT for a full day.
They have a proj "build 4 Ukraine"

Serhii Ivanets -- dean of master's engineering will be here with us for 2 hours

\begin{notebox}
    Get details about the master's program
\end{notebox}

\subsection{Research questions}

We have a goal and some high level questions. We must agree on how our results look like so all outputs are compatible.
Nastsasia has a draft.

\textbf{My 3 questions}

\begin{enumerate}
    \item What type of engineer (civil, space, etc) would you like to become and what do you think you have to master to get there?
    \item What are top 3 reasons you want to become an engineer?
    \item If you could change one thing in Ukrainian education system what would it be?
\end{enumerate}

\textbf{Questions about enabling environment}

\begin{enumerate}
    \item Do you collaborate with your fellows on non-university related projects?
    \item Where (if anywhere) do you phisically go when you want to learn or try out your ideas?
    \item What extracurricular activities in your opinion are most valuable for your professional growth?
    \item Do you feel that you that your university supports/encourages student-led activities/clubs?
    \item How important is peer-to-peer knowledge acquisution for you?
\end{enumerate}

