\renewcommand{\chaptertitle}{Research, Design Nature}
\setdate{Sepember 11, 2025}
\section{\chaptertitle}


\subsection{Research}

Today I came lately, didn't note much. We re-wrote the questionnaire from scratch and agreed on the set of questiobs.
Then each team presented their progress (10 mins each)

\subsection{A call with Timur}

We updated him on our research.
Once we have groups then we can talk about classes.
There are different options. We all will be in DN\footnote{Henceforth -- Design Nature}. We can't get full classes due to limited time. So we split into different classes according to our interests.

Student are allowed to make mistakes with equipment that costs \$100k+ and that's what makes them unique.
There's a curriculum review in Olin. They are not quite new school anymore (25 yo now).
Each student chooses a class that they want ot change and spend a semester on it. They are removing grading -- one of the most extreme ones.

In Olin instead of Teaching Instructors (TI) they have $\to$ Course Instructors (CI)
Timur will send us a microsoft form to better match us with a student at Olin who we will be "attached to".

Olin students do a lot of extracurricular projects. 

\begin{notebox}
    (adj.) prosthetic -- add to Anki
\end{notebox}

An Olin student who just graduated has as good soft skills as other graduates who are 5+ years in the workforce.

General Engineering includes Bio Engineering. Timur has chosen Mechanical Engineering.

Cocuricular -- a class you take not for credits.

MIT Create Challenge --  a challenge MIT does each year. Build 4 Ukraine first time -- last year. What if we get undergrads in a room to solve a problem currently going in Ukraine.

It's possible that a few students from Olin will be working for us in KSE.

\subsection{Design Nature}

The audio was shit.
Couldn't take any note whatsoever. Will ask Oleg for his Cluely's summary.


