\renewcommand{\chaptertitle}{Homework 2}
\setdate{Sepember 14, 2025}
\section{\chaptertitle}


I am going to Olin College because I want to experience firsthand how engineering education can be built around projects, teamwork, and creativity. At the Kyiv School of Economics, we are working to adapt this approach to Ukraine, and for me it is important not just to read about it, but to live inside that culture for a few weeks. By being at Olin, I hope to see how students and CAs, how they organize their learning, and how project-based education looks in daily practice.

What I want most from this trip is perspective. I want to compare how Olin students think about engineering with how we, in Ukraine, are used to thinking about it. I hope to learn not only about the technical side of their projects, but also about the values that shape them: collaboration, responsibility, and openness. I believe that these values are as important for a modern engineer as the knowledge of equations and tools.

I also see this trip as a way to grow personally. By immersing myself in a different academic culture, I will test my own ability to adapt, to work in international teams, and to communicate my ideas clearly. I want to bring back not just methods, but also inspiration — the kind of mindset that can motivate students in Ukraine to see engineering as a living, creative practice.

Ultimately, I hope this experience will make me a bridge between Olin and KSE. I want to return with concrete stories, examples, and practices that can help us build a program where students learn by doing, by experimenting, and by shaping the world with their own hands.