\renewcommand{\chaptertitle}{Prepare for Olin}
\setdate{Sepember 15, 2025}
\section{\chaptertitle}

\subsection{A new one \& Rebecca's update}

Mykyta came a bit late with a new guy. 
He has tatoos on the right forearm and earrings. 
Probably a new partner student... No, 
I just learned that his name is Pavlo Bilyk and he is teaching urban studies at KSE.
And he is (kind of?) faculty. 
He is going to Olin with us. 
He remembers Oleg from our call with Olin during summer studio.

Rebecca is going to Montreal on Thursday. Some updates from her. 
No-one else was able to join Olin to the extent we did.
Buddy system -- each one will have a "buddy" while we are there.
If someone (like me??) doesn't have one yet they will get one soon.
Masha Alipatova's buddy is Jessy -- responsible for mechanical engineering.

\begin{notebox}
    AHS -- arts, humanities, and social sciences.
\end{notebox}

A professor from Scotland will meet us there to explain
how maths is integrated in project-based learning.

All partner students will be included to design nature course. Also we can take one (may be more) additional course to follow during all the time.
We will also have mini (condensed) lectures. We'll have an opportunity to work in the workshop.

SCOPE project has been cancelled. SCOPE is a capstone project. 

They're trying hard to make us stay at dorms (meybe not Olin but Babson).

\begin{notebox}
    We have to determine who is responsible for what during Olin trip.
\end{notebox}

Mariia Kriuchok mentioned that we should not only absorb everything there.
We should also share something about us.

Here's an excercise (choose one weakness and figure out who knows how to and can help) given by Nastasya:

\begin{definition}{What I struggle with \& how to achieve it}{}
    Better technique to be able to tackle Oleg in fistfight.

    Oleg has it in profusion.
\end{definition}

\subsection{Research \& closing}

Removed some questions.

We need to finish the research till Friday and present our portraits.




