\renewcommand{\chaptertitle}{Research presentation}
\setdate{Sepember 19, 2025}
\section{\chaptertitle}

My task for presentation preparation is aggregating responses and making a list of hard competences that an engineer should have.

Here's the list:
\begin{enumerate}
    \item Maths. Especially calculus, differential equations, Fourier transformation, to name a few. It should be taught in a gradual way with moderate increase in difficulty and also be connected with engineering tasks at hand not purely theoretical.
    \item Same for physics and theoretical mechanics.
    \item Programming. Python for everyone, C++ for microcontrollers, MATLAB for simulations.
    \item Ability to estimate costs (in terms of money, time, resources, etc.) that an engineering project requires, and ability to reduce them with optimal compromise of the quality of the result.
    \item English language. German language (I just love German). 
    \item Skills with electronics, soldering, 3D printing
\end{enumerate}


For Mariia:

I learned that sciences are taught very well in our universities. 
The problem is that it's all disintegrated. 
An engineer must be able to estimate costs and to find optimal compromises between quality and prices.
"One can build two expensive top-notch bombarders \$2B each or an entire fleet of simply decent ones".
Students must be well versed because it's not enough to be technical, one must be humane.
Each student must learn collaborative work and leadership through projects. 
Because at the moment we have a paradigm "the one who is the smartest becomes a leader and does almost all work".

\subsection{Update about DN}

Monday 9:20 - 12:00 -- Design Nature

Each of us will have a buddy

There will be a homework: amass some knowledge prior. 

Three points:

- Learn about bio hopper through sketching\\
- Sketch a hopper\\
- Think about materials 

\subsection{Plan for Monday}

On Monday we plan to decide who is responsible for what.
We will be assigning responsibilities to each person -- what they should do while in Olin.

