\renewcommand{\chaptertitle}{Monday}
\setdate{Sepember 29, 2025}
\section{\chaptertitle}

\subsection{A meeting in 428}

Lynn knows
\begin{notebox}
    Where most of the bodies are burried
\end{notebox}

She has been here from the beginning. 

Zhenya is from Ukraine. She understands ukrainian.
She lived on Volodymyrska street.


Timur is somewhere between mechanical and bio-mechanical engineering.

\subsection{Design Nature W5}

% Avoid elevators this morning since the lector got stuck today.

\textbf{Parametric design and Experimental prototyping}

How do changes in parameters effect brhaviour or perfomance?

what is flax egg?

an experimental prototype is not a test prototype.
design for experiments. phollow (sic!) the physics.

how to run a parametrix experiments?

- simulations

something is difficult to simulate:
friction, damping, material properties

if you havent' built it it doesn't work

what: flips (x2), trigger release, jump height (x2)

how: vary leg lengthmove CM with different tails, many attachment holes, rubber tube length, total weight

\textbf{Confounding parameters}

change one param at a time.

success involves a lot of learning so a lot of experiments.

\textbf{Stress concentration}

$Stress(\sigma) = \frac{Force}{Area}$

force 'flow' lines bnch together means higher stress.

SolidWorks simulation (finite element analysis)

stress concentration factor, knows

to avoid failures:

- fillets beter than sharp edges

- move holes away from edges

- increase size of parts under stress

- large cross-sections to reduce stress

kerf (thickness) for laser cutter

leave very little space between parts only about .01" of space

keep a buffer on the right

what are crosshairs?

no raster or vector etching.

all the slides are posted on the website.

\subsection{Design better drugs}

At the beginning a strange song (hello I'm an enzyme) about proteins, enzymes, etc was turned on and we were asked to sing along. I didn't.

I realised that only I will be profoundly integrated in the course.

\begin{notebox}
    what is an allosteric inhibitor?
\end{notebox}


how is cell signaling involved in migrane headaches?

secondary messengers?

how does an epi pen shut down anaphylaxis?

\begin{definition}{anaphylaxis}{}
    severe immune reaction to an allergene
\end{definition}

mast cells?

monomers: amino acids, nucleotides, monosaccarides -- increased entropy

a peptides (polymers)

anabolism/catabolism

what is an assay?? substrate?

then we did a lab. I had a chance to do several things myself.
met Charith and Jake whom I was shadowning mostly. 
Jake is also in Formula's team and invited me to 
visit their meeting later today.
also talked to the teacher (the guy). talked about Malthus
I learned from him that all (even somatic) cells can express genes in different environments.
Charith shared their textbook with me after the class.
