\renewcommand{\chaptertitle}{Tuesday}
\setdate{Sepember 30, 2025}
\section{\chaptertitle}

\subsection{QEA 1}


I attended this class with Oleg. This was basically linear algebra. We were given sheets with tasks.
They are filled with some matrix problems. Each group of students
were solving them collectively.
I sat on a table with two girls. One of them 
is really good at maths and would have loved to 
major maths but if she went to undergrad maths then she would have to go to grad maths and then she
wouldn't be able to do tangible things which she would like.
The second one is more into engineering and not so much into 
abstract math. By the way she doesn't live in the dorms
because she lives close to the college and drives there. And if
I understood correctly, this has implications like she can't eat 
at the dining hall for free like others. Spent most of the class
talking to them about lots of different things.


\subsection{6 books that changed the world}

The task was to make a collage. I didn't quite get it.
I talked to the lecturer (Bob or Rob) from the first day in Olin.
I quessed the first book (after I said Martin Eden).
And then the second one (after I tried On the Wealth of Nations).

\textbf{The booklist:}
\begin{enumerate}
    \item On the Origin of Species (3)
    \item Das Kapital (1)
    \item The Feminine Mistique (4)
    \item Uncle Tom's cabin (2)
    \item Choice: Silent Spring or The Epic of Gilgamesh (5)
    \item Book 6: Project -- A book of my choice
\end{enumerate}

\subsection{Probabilistic modeling}

There was a test during the entire class. All the problems
were easily solved with Bayes' formula so it was 
not a rocket science.

